---
output: 
  github_document:
    toc: TRUE
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Part 1: ma206data goals and examples

<!-- badges: start -->
<!-- badges: end -->

The goal of ma206data is to make the 'Introduction to Statistical Investigations, Edition II' datasets and other course data sets quickly accessible in R.

``` r
remotes::install_github("EvaMaeRey/ma206data")
```

## chap2_Coffee example

```{r example, message = F, warning=F}
library(tidyverse)
library(ma206data)
## basic example code

chap2_Coffee %>% head()


chap2_Coffee %>% 
  ggplot() +
  aes(cups_per_week) + 
  geom_rug() + 
  geom_histogram()
```

## chap10_CatJumpingFull example

```{r}
chap10_CatJumpingFull %>% 
  ggplot() + 
  aes(x = body_mass_g, 
      y = takeoff_velocity_cm_sec, 
      color = sex_0_f_1_m) + 
  geom_point()
```

## cd (course director) example

tbd.

```{r}
```




# Part 2: Project management

Most of the action happens in the data-raw folder scripts and folders.



```{r}
fs::dir_ls("data-raw/")
```
1. Gathering data: 

- The folder [**data-raw/course_director_data**](https://github.com/EvaMaeRey/ma206data/tree/master/data-raw/course_director_data) is populated manually with csvs
- The folder [**data-raw/isi_txt_data**](https://github.com/EvaMaeRey/ma206data/tree/master/data-raw/isi_txt_data) is populated automatically using the script [**data-raw/01_scrape_isi_ed2.R**](https://github.com/EvaMaeRey/ma206data/blob/master/data-raw/01_scrape_isi_ed2.R)

2. Converting to native R format and saving to package's 'data' folder using:

- [**data-raw/02_save_course_director_data_as_rda_for_package.R**](https://github.com/EvaMaeRey/ma206data/blob/master/data-raw/02_save_course_director_data_as_rda_for_package.R)
- [**data-raw/02_save_isi_data_as_rda_for_package.R**](https://github.com/EvaMaeRey/ma206data/blob/master/data-raw/02_save_isi_data_as_rda_for_package.R)

3. Document the datasets by running:

- [**data-raw/03_write_dataset_minimal_documentation.R**](https://github.com/EvaMaeRey/ma206data/blob/master/data-raw/03_write_dataset_minimal_documentation.R) is executed, which creates, the file [**data/datasets_listed.R**](https://github.com/EvaMaeRey/ma206data/blob/master/data/datasets_listed.R) which documents (minimally) the datasets for the package, making them usable.



# Part 3. All datasets listed

```{r}
data(package = "ma206data", verbose = T)$results[,"Item"]
```
